Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-02-04 causal-bandit/icml-2015/discussion.tex
More on discussion

\todom{Still cleaning up below}
\paragraph{Cumulative Regret}

@@

\paragraph{Causal Models with Non-Observable Variables}
In this case, some queries will be non-identifiable. The corresponding actions can be immediately added to the set $A$ prior to collecting any data. We can then use the same algorithm as in the case where there are no latent variables, except that we will have to use the more general do-calculus rather than simply adjusting for the parents to write the expression for each action in terms of observational data. 
%

@@

\paragraph{Partially or Completely Unknown Causal Graph}

Unknown in general case - e.g., like algorithm 1

(Partially known structure)
There has been substantial work on the problem of selecting experiments to discover the correct causal graph from within a Markov equivalence class \cite{Eberhardt2005,eberhardt2010causal,hauser2014two,Hu2014}. This problem arises naturally if we assume free access to a large observational dataset, from which the Markov equivalence class can be found via causal discovery techniques. Key results $bigo(n)$ singleton or $bigo(log log n)$ multi-variate experiments are required.
- Focus on minimizing the number of experiments that must be performed. Examples of active versus online learning. The cost of experiments constant or at least known.

(Unknown Structure)
If we need to learn the structure, in an online environment. 
Experiment is much, much more revealing than inference from observational data. We would expect it to dominate.

>>>>

\paragraph{Cumulative Regret}
Another open question is whether cumulative regret bounds can be obtained for the general causal bandit problem we have proposed.
In the case of the parallel bandit problem however, we can make use of existing work on bandits with graph feedback to achieve this.
Each time an action $do(X_i = j) \in \calA$ is chosen

@@

\paragraph{Causal Models with Non-Observable Variables}
We have assumed through this paper that all variables in the causal model were observable after an intervention is made.
A natural generalisation of our model would be for some variables to be unobservable.
In this case, some conditional distributions may be non-identifiable. 
The corresponding actions can be immediately added to the set $A$ prior to collecting any data. 
We can then use the same algorithm as in the case where there are no latent variables, except that we will have to use the more general do-calculus rather than simply adjusting for the parents to write the expression for each action in terms of observational data. 
%

@@

\paragraph{Partially or Completely Unknown Causal Graph}
A much more difficult generalisation would be to consider causal bandit problems where the causal graph is completely unknown or known to be a member of class of models.
The latter case arises naturally if we assume free access to a large observational dataset, from which the Markov equivalence class can be found via causal discovery techniques. 
Work on the problem of selecting experiments to discover the correct causal graph from within a Markov equivalence class~\cite{Eberhardt2005,eberhardt2010causal,hauser2014two,Hu2014} could potentially be incorporated into a causal bandit algorithm as part of a pre-processing step.
Simultaneously learning a completely unknown causal model while estimating the rewards of interventions would be much more challenging.
\todom{Ideas? Relevant refs?}

% (Partially known structure)
% Key results $bigo(n)$ singleton or $bigo(log log n)$ multi-variate experiments are required.
% - Focus on minimizing the number of experiments that must be performed. Examples of active versus online learning. The cost of experiments constant or at least known.

% (Unknown Structure)
% If we need to learn the structure, in an online environment. 
% Experiment is much, much more revealing than inference from observational data. We would expect it to dominate.
